\documentclass{article}
\usepackage[a4paper, total={7in, 10in}]{geometry}
\usepackage{hyperref}
\pagenumbering{gobble}
\input{glyphtounicode}
\pdfgentounicode=1
\begin{document}

% title and contact information
\title{\vspace{-1.5cm}\textbf{Ridvik Pal}\vspace{-1.5cm}}
\date{}
\maketitle
\begin{center}
    (+1) 647-808-4531
    \hfill
    \href{mailto:ridvik.pal@outlook.com}{\underline{ridvik.pal@outlook.com}}
    \hfill
    Ontario, Canada
    \hfill
    \href{https://github.com/ridvikpal}{\underline{github.com/ridvikpal}}
    \hfill
    \href{https://www.linkedin.com/in/ridvik-pal}{\underline{linkedin.com/in/ridvik-pal}}
\end{center}

% skills section
\section*{Skills}
\textbf{Languages:} Python, Java, C++, SQL, Microsoft VBA, \LaTeX \\
\textbf{Tools:} MySQL, PostgreSQL, Git, GitHub, Microsoft Excel, Maven \\
\textbf{Frameworks/Libraries:} Spring Boot, JavaFX, Qt, Pandas, Plotly, Matplotlib \\
\textbf{Concepts:} DevOps, REST APIs, Debugging, Multithreading, Engineering Design

% education section
\section*{Education}
\subsection*{University of Toronto \hfill \normalfont{\textit{Sep 2021 - May 2026}}}
B.A.Sc. in Computer Engineering with Minor in Artificial Intelligence (AI) and Business

% work experience section
\section*{Work Experience}
\subsection*{Intern Software Engineer \hfill \normalfont{\textit{May 2024 - August 2025}}}
\textit{Xero - Toronto, ON}
\begin{itemize}
    \item 
\end{itemize}

\subsection*{SEO IT Systems Assistant \hfill \normalfont{\textit{May 2023 - Sep 2023}}}
\textit{Ministry of the Solicitor General - Toronto, ON}
\begin{itemize}
    \item Automated creation of Excel database worksheets by programming VBA scripts, saving hours of work time each day.
    \item Generated daily data analytics reports processing, validating, and cleaning thousands of lines of raw data on the operation of Cisco codecs utilizing Excel power queries.
    \item Created and updated data for thousands of configuration items (CIs) in the configuration management database (CMDB) via the BMC Remedy Asset Management Console.
    \item Updated and managed project documentation for hundreds of projects.
\end{itemize}

\subsection*{Mathematics, Physics, and Computer Science Tutor \hfill \normalfont{\textit{May 2022 - Current}}}
\textit{Varsity Tutors - Remote}
\begin{itemize}
    \item Tutored over 60 students ranging from high school to university level, specializing in mathematics, physics, and computer science.
    \item Am currently a 5-star rated tutor on the platform, receiving glowing recommendations from students and their parents.
\end{itemize}

% projects section
\section*{Projects}
\subsection*{CarCartAPI}
\textit{REST APIs, Java, Spring Boot, MySQL, Spring MVC, Maven, Git}
\begin{itemize}
    \item Java Spring Boot REST API that retrieves used car listings, updates used car listings, and provides car information using the ChatGPT 3.5 Turbo AI Model.
    \item Supports GET, PUT, POST, DELETE requests with fully multithreaded calls.
\end{itemize}

\subsection*{RainyDay}
\textit{Java, JavaFX, Maven, CSS, REST APIs, Git}
\begin{itemize}
    \item Java weather app built using a JavaFX GUI and a custom modular backend weather API.
    \item Supports current and future weather for over 1,000,000 cities, weather alerts, user notifications, 15 different light/dark themes and touch input.
\end{itemize}

\subsection*{MarkedUp}
\textit{Python, Virtual Environments, REST APIs, PyQt5, Plotly, Pandas, Git}
\begin{itemize}
    \item Python desktop stock market app inspired by Yahoo Finance, built using the TwelveData REST API and PyQT5 GUI library.
    \item Supports stock quotes for over 20,000 stocks, interactive candlestick charts, smart autocomplete equity search, favourites watchlist, a custom GUI with light/dark themes, and internal multithreading.
\end{itemize}

\subsection*{SimplyTrack}
\textit{Python, MySQL, PySimpleGUI, Matplotlib, AES Encryption, Git}
\begin{itemize}
    \item Python Financial tracker app that stores financial data in a MySQL database with a GUI built in PySimpleGUI.
    \item Supports AES 256-bit encryption, data visualization with matplotlib, csv data import, a custom GUI with light/dark themes, bulk data modification and manual data entry.
\end{itemize}

\subsection*{MatchMap}
\textit{C++, GTK3, Make, Git, Linux}
\begin{itemize}
    \item C++ GIS mapping software built using the OpenStreetsMap database and GTK3 GUI library.
    \item Supports complete car routing, 19 international cities, multithreading, distinct colour scheme, a custom GUI with light/dark themes, and advanced search features.
\end{itemize}

\end{document}